Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-10-14 Supplemental-Material-A-Annotated-Analysis.Rmd
Update Supplemental-Material-A-Annotated-Analysis.Rmd

```{r kmeans determin k}
# prepare data for main analysis
raw_data <- featData
z_data <- featFullImp$featuresImpZ
scaled_data <- featFullImp$featuresImpZMat

@@

scaled_data <- featFullImp$featuresImpZMat

@@

```{r MClust feature specific cluster numbers}
nMClust <- list()
for(f in unique(gsub("^.*?\\_", "", names(featFullImp$featuresImpZMat)))){
  scaled_data <- featFullImp$featuresImpZMat %>% select(ends_with(f))
  mod1 <- Mclust(scaled_data)
  #summary(mod1, parameters = FALSE)
  nMClust[[f]] <- mod1$G
}

nMClust %>%
  unlist %>%
  data.frame(feature=names(.), G=., row.names=NULL) %>%
  kbl(.,
      escape = FALSE,
      booktabs = T,
      align = c("l", "c"),
      digits=2,
      col.names = c(
        "Feature",
        "Number of Clusters"
      ),
      caption = "Number of MClust Clusters if separated by Feature") %>%
  kable_classic(
    full_width = F,
    lightable_options = "hover",
    html_font = "Cambria"
  )
```

@@

#scaled_data <- featFullImp$featuresImpZMat %>% select(starts_with(varNamS123Int))
scaled_data <- featFullImp$featuresImpZMat  # %>% select(starts_with(varNamS123NoInt))#%>%
  #select(-any_of(names(which(colSums(is.na(scaled_data)) > 0))))

@@

# to plot the eps values
eps_plot = kNNdistplot(scaled_data, k=3)
# to draw an optimum line
eps_plot %>% abline(h = 15, lty = 2)

potentialMinPts <- round(SciViews::ln(nrow(scaled_data)))
eps <- 15
minPts <- 2

@@

```{r dbscan feature specific cluister numbers}
minPts <- 3
xi <- 0.04 #0.05
nDbscan <- list()
for(f in unique(gsub("^.*?\\_", "", names(featFullImp$featuresImpZMat)))){
  scaled_data <- featFullImp$featuresImpZMat %>% select(ends_with(f))
  #res.fpc <- dbscan::dbscan(scaled_data, eps=eps_cl, MinPts=minPts)

>>>>

```{r kmeans determin k}

featureExclusion <- c(
  "mean",
  "sd",
  "rmssd",
  "ar02",
  "edf_ar"
)

# prepare data for main analysis
raw_data <- featData
z_data <- featFullImp$featuresImpZ %>% select(-ends_with(featureExclusion))
scaled_data <- featFullImp$featuresImpZMat %>% select(-ends_with(featureExclusion))

@@

scaled_data <- featFullImp$featuresImpZMat %>% select(-ends_with(featureExclusion))

@@

```{r MClust feature specific cluster numbers}
scaled_data <- featFullImp$featuresImpZMat %>% select(-ends_with(featureExclusion))
nMClust <- list()
for(f in unique(gsub("^.*?\\_", "", names(scaled_data)))){
  scaled_data <- featFullImp$featuresImpZMat %>% select(ends_with(f))
  mod1 <- Mclust(scaled_data)
  #summary(mod1, parameters = FALSE)
  nMClust[[f]] <- mod1$G
}

nMClust %>%
  unlist %>%
  data.frame(feature=names(.), G=., row.names=NULL) %>%
  kbl(.,
      escape = FALSE,
      booktabs = T,
      align = c("l", "c"),
      digits=2,
      col.names = c(
        "Feature",
        "Number of Clusters"
      ),
      caption = "Number of MClust Clusters if separated by Feature") %>%
  kable_classic(
    full_width = F,
    lightable_options = "hover",
    html_font = "Cambria"
  )

@@

#scaled_data <- featFullImp$featuresImpZMat %>% select(starts_with(varNamS123Int))
scaled_data <- featFullImp$featuresImpZMat %>% select(-ends_with(featureExclusion))  # %>% select(starts_with(varNamS123NoInt))#%>%
  #select(-any_of(names(which(colSums(is.na(scaled_data)) > 0))))

@@

# to plot the eps values
eps_plot = kNNdistplot(scaled_data, k=3)
# to draw an optimum line
eps_plot %>% abline(h = 11, lty = 2)

potentialMinPts <- round(SciViews::ln(nrow(scaled_data)))
eps <- 11
minPts <- 2

@@

```{r dbscan feature specific cluister numbers}
scaled_data <- featFullImp$featuresImpZMat %>% select(-ends_with(featureExclusion))
minPts <- 3
xi <- 0.04 #0.05
nDbscan <- list()
for(f in unique(gsub("^.*?\\_", "", names(scaled_data)))){
  scaled_data <- featFullImp$featuresImpZMat %>% select(ends_with(f))
  #res.fpc <- dbscan::dbscan(scaled_data, eps=eps_cl, MinPts=minPts)
